An quasi-consistent efficient meshfree thin shell formulation naturally accommodating essential boundary conditions

### 2024-02-14 boundary.tex
last night

\section{Naturally variational enforcement for essential boundary conditions}

@@

- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
- \sum_{C=1}^{n_e}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} = \boldsymbol f_I

@@

and further substituting coefficients $\boldsymbol d_N^\alpha$, $\boldsymbol d_M^{\alpha\beta}$ into Eq. (\ref{w51}) gives the final discrete equilibrium equations: 

@@

&- \sum_{C=1}^{n_c}(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
- \sum_{C=1}^{n_c}(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \\
= &\sum_{C=1}^{n_e} \sum_{J=1}^{n_p} \left (

@@

& \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \tilde{\boldsymbol g}_{\eta J} 
+ \tilde{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \tilde{\boldsymbol g}_{\gamma\eta} \\
- & \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \tilde{\boldsymbol g}_{\eta J} - \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \bar{\boldsymbol g}_{\eta J} \\
- & \bar{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \tilde{\boldsymbol g}_{\gamma\eta J} - \tilde{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \bar{\boldsymbol g}_{\gamma\eta J} \\
+ & \boldsymbol a_\alpha \tilde{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \hat{\boldsymbol g}_{\eta J}
- \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \hat{\boldsymbol g}_{\eta J} \\
+ & \tilde{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \hat{\boldsymbol g}_{\gamma\eta J} - \bar{\boldsymbol g}^T_{\alpha\beta I} \boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \hat{\boldsymbol g}_{\gamma\eta J} \\
+ & \boldsymbol a_\alpha \bar{\boldsymbol g}^T_{\beta I} h C^{\alpha\beta\gamma\eta} \boldsymbol a_\gamma \bar{\boldsymbol g}_{\eta J}
+ \bar{\boldsymbol g}^T_{\alpha\beta I}\boldsymbol a_3 \frac{h^3}{12} C^{\alpha\beta\gamma\eta} \boldsymbol a_3 \bar{\boldsymbol g}_{\gamma\eta J} 

@@

\right ) \\
= &\sum_{J=1}^{n_p} (\boldsymbol K_{IJ}+\tilde{\boldsymbol K}_{IJ}+\bar{\boldsymbol K}_{IJ}) \cdot \boldsymbol d_J - \tilde{\boldsymbol f}_I - \bar{\boldsymbol f}_I

@@

        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} \tilde{\boldsymbol N}^{\alpha\beta}_J d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \tilde{\boldsymbol M}^{\alpha\beta}_J d\Omega

@@

        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol t}_J + \tilde{\boldsymbol t}_I \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde M_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
                                     & + ([[\Psi_I \boldsymbol a_3 P_J]] + [[P_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}

@@

\tilde{\boldsymbol f}_I = &- \int_{\Gamma_v} \tilde{\boldsymbol t}_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \tilde M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\tilde P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

\bar{\boldsymbol K}_{IJ} &= - \int_{\Gamma_v} \bar{\boldsymbol t}_I \Psi_J d\Gamma 
+ \int_{\Gamma_\theta} \boldsymbol a_3\bar M_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma d\Gamma + [[\bar P_I \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
\bar{\boldsymbol f}_I &= - \int_{\Gamma_v} \bar{\boldsymbol t}_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \bar M_{\boldsymbol{nn}} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\bar P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix. As shown in these equations, the Eq. (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs. (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary.

@@

\begin{subequations}

@@

        \boldsymbol K^c_{IJ} &= -\int_{\Gamma_v} \left ((\boldsymbol {\mathcal T}^\alpha \Psi_{I,\alpha} + \boldsymbol{\mathcal V}^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta) \Psi_J + \Psi_I (\boldsymbol {\mathcal T}^\alpha \Psi_{J,\alpha} + \boldsymbol{\mathcal V}^{\alpha\beta}\Psi_{J,\alpha}\vert_\beta)\right ) d\Gamma \\
                             &+ \int_{\Gamma_M} (\mathcal M^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta \boldsymbol a_3 \Psi_{J,\gamma}n^\gamma + \Psi_{I,\gamma}n^\gamma \boldsymbol a_3 \mathcal M^{\alpha\beta} \Psi_{I,\alpha}\vert_\beta) d\Gamma

@@

>>>>

\section{Naturally variational enforcement for essential boundary conditions}\label{boundary}

@@

- \sum_{C=1}^{n_e}\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \left ( (\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d_N^{\alpha}
+ (\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d_M^{\alpha\beta} \right ) = - \sum_{I=1}^{n_p}\delta d_I \cdot \boldsymbol f_I

@@

the left side of Eq. (\ref{w51}) can be simplified by following steps. For clarity, the derivation of first term in Eq. (\ref{w51}) regarding as an example is given by:

@@

\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \tilde{\boldsymbol g}^T_{\alpha I} \boldsymbol d_N^\alpha 
&= \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol G \boldsymbol d^\alpha_N \\
&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot (\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  \boldsymbol q^T \boldsymbol d^\alpha_N d\Omega \\
&= \int_{\Omega_C} \sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot \boldsymbol a_\beta(\boldsymbol q^T\boldsymbol G^{-1} \tilde{\boldsymbol g}_{\alpha I})^T  N^{\alpha\beta h} d\Omega \\
& = \int_{\Omega_C} \delta \tilde \varepsilon_{\alpha\beta}^h N^{\alpha\beta h} d\Omega 
following the above procedure and including the weak form of Eqs. (\ref{w1}), (\ref{w2}), the left side of Eq. (\ref{w51}) in $\Omega_C$ becomes:

@@

&\sum_{I=1}^{n_p} \delta \boldsymbol d_I \cdot  \left ( 
(\tilde{\boldsymbol g}^T_{\alpha I} - \bar{\boldsymbol g}^T_{\alpha I}) \boldsymbol d^\alpha_N
+(\tilde{\boldsymbol g}^T_{\alpha\beta I} - \bar{\boldsymbol g}^T_{\alpha\beta I}) \boldsymbol d^{\alpha\beta}_M \right) \\
=& \int_{\Omega_C}\left ( (\delta \tilde \varepsilon^h_{\alpha\beta} - \delta \bar \varepsilon^h_{\alpha\beta}) N^{\alpha\beta h}
+ (\delta \tilde \kappa^h_{\alpha\beta} - \delta \bar \kappa^h_{\alpha\beta})M^{\alpha\beta h}
\right ) d\Omega \\
= &\int_{\Omega_C} (\delta \tilde \varepsilon^h_{\alpha\beta} - \delta \bar \varepsilon^h_{\alpha\beta}) hC^{\alpha\beta\gamma\eta} \varepsilon^h_{\gamma\eta}
+ (\delta \tilde \kappa^h_{\alpha\beta} - \delta \bar \kappa^h_{\alpha\beta}) \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\kappa^h_{\gamma\eta} \\
= &\int_{\Omega_C}\delta \tilde \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \tilde\varepsilon^h_{\gamma\eta} d\Omega
+ \int_{\Omega_C}\delta \tilde \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\tilde \kappa^h_{\gamma\eta}d\Omega \\
- &\int_{\Omega_C}\delta \tilde \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \bar \varepsilon^h_{\gamma\eta} d\Omega
- \int_{\Omega_C}\delta \bar \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \tilde \varepsilon^h_{\gamma\eta} d\Omega \\
- &\int_{\Omega_C}\delta \tilde \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\bar \kappa^h_{\gamma\eta}d\Omega 
- \int_{\Omega_C}\delta \bar \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\tilde \kappa^h_{\gamma\eta}d\Omega \\
+ &\int_{\Omega_C}\delta \bar \varepsilon^h_{\alpha\beta}hC^{\alpha\beta\gamma\eta} \bar \varepsilon^h_{\gamma\eta} d\Omega
+ \int_{\Omega_C}\delta \bar \kappa^h_{\alpha\beta} \frac{h^3}{12}C^{\alpha\beta\gamma\eta}\bar \kappa^h_{\gamma\eta}d\Omega \\
+ &\int_{\Omega_C}(\delta \tilde \varepsilon^h_{\alpha\beta} - \delta \bar \varepsilon^h_{\alpha\beta})hC^{\alpha\beta\gamma\eta} \hat \varepsilon^h_{\gamma\eta} d\Omega
+ \int_{\Omega_C}(\delta \tilde \kappa^h_{\alpha\beta} - \delta \bar \kappa^h_{\alpha\beta})\frac{h^3}{12}C^{\alpha\beta\gamma\eta}\hat \kappa^h_{\gamma\eta}d\Omega \\

@@

and further substituting Eqs. (\ref{epsilon2}), (\ref{kappa2}) into above equation gives the final discrete equilibrium equations: 
        (\boldsymbol K + \tilde{\boldsymbol K} + \bar{\boldsymbol K} )\boldsymbol d = \boldsymbol f + \tilde{\boldsymbol f} + \bar{\boldsymbol f}

@@

        \boldsymbol K_{IJ} = \int_\Omega \tilde{\boldsymbol \varepsilon}_{\alpha\beta I} hC^{\alpha\beta\gamma\eta}\tilde{\boldsymbol \varepsilon}_{\gamma\eta J} d\Omega + \int_\Omega \tilde{\boldsymbol \kappa}_{\alpha\beta I} \frac{h^3}{12}C^{\alpha\beta\gamma\eta} \tilde{\boldsymbol \kappa}_{\alpha\beta J} d\Omega

@@

        \tilde{\boldsymbol K}_{IJ} = &- \int_{\Gamma_v} (\Psi_I \tilde{\boldsymbol T}_{NJ} + \tilde{\boldsymbol T}_{NJ} \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}J} + \boldsymbol a_3 \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
                                     & + ([[\Psi_I \boldsymbol a_3 \tilde{\boldsymbol P}_J]] + [[\tilde{\boldsymbol P}_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}

@@

\tilde{\boldsymbol f}_I = &- \int_{\Gamma_v} \tilde{\boldsymbol T}_{NI} \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \tilde{\boldsymbol M}_{\boldsymbol{nn}I} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\tilde{\boldsymbol P}_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

\bar{\boldsymbol K}_{IJ} &= - \int_{\Gamma_v} \bar{\boldsymbol T}_{MI} \Psi_J d\Gamma 
+ \int_{\Gamma_\theta} \boldsymbol a_3\bar{\boldsymbol M}_{\boldsymbol{nn}I} \Psi_{J,\gamma}n^\gamma d\Gamma + [[\bar{\boldsymbol P}_I \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
\bar{\boldsymbol f}_I &= - \int_{\Gamma_v} \bar{\boldsymbol T}_{MI} \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \bar{\boldsymbol M}_{\boldsymbol{nn} I} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\bar{\boldsymbol P}_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

The detailed derivations of Eqs (\ref{de1})-(\ref{de3}) are listed in the Appendix \ref{derivations}. As shown in these equations, the Eq. (\ref{de1}) is the conventional stiffness matrix evaluated by smoothed gradients $\tilde \Psi_{I,\alpha}$, $\tilde \Psi_{I,\alpha}\vert_\beta$, and the Eqs. (\ref{de2}) and (\ref{de3}) contribute for the enforcement of essential boundary. It should be mentioned that, in accordance with reproducing kernel smoothed gradient framework, the integration scheme of Eqs. (\ref{de1}-\ref{de3}) should be aligned with the those used in the construction of smoothed gradients. With a close look with Eqs. (\ref{de2}) and (\ref{de3}), the proposed approach for enforcing essential boundary conditions show an identical structure with traditional Nitsche's method, both have the consistent term and stabilized term. So the next subsection will review the Nitsche's method and compare it with proposed method.

@@

\begin{subequations}\label{nde2}

@@

\boldsymbol K^c_{IJ} = &- \int_{\Gamma_v} (\Psi_I \boldsymbol T_{NJ} + \boldsymbol T_{NJ} \Psi_J) d\Gamma \\
                                     &+ \int_{\Gamma_\theta} (\Psi_{I,\gamma} n^\gamma \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}J} + \boldsymbol a_3 \boldsymbol M_{\boldsymbol{nn}I} \Psi_{I,\gamma}n^\gamma)d\Gamma \\
                                     & + ([[\Psi_I \boldsymbol a_3 \boldsymbol P_J]] + [[\boldsymbol P_I \boldsymbol a_3 \Psi_J]])_{\boldsymbol x \in C_v}
\boldsymbol f^c_I = &- \int_{\Gamma_v} \boldsymbol T_I \cdot \bar{\boldsymbol v} d\Gamma + \int_{\Gamma_\theta} \boldsymbol M_{\boldsymbol{nn}I} \bar{\theta}_{\boldsymbol n} d\Gamma + [[\boldsymbol P_I\boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

@@

\begin{subequations}\label{nde3}
\boldsymbol K^s_{IJ} &= \alpha_v \int_{\Gamma_v} \Psi_I \Psi_J \boldsymbol 1 d\Gamma 
+ \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol a_3 n^\gamma\Psi_{J,\gamma} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \Psi_J]]_{\boldsymbol x \in C_v} \\
\boldsymbol f^s_I &= \alpha_v \int_{\Gamma_v} \Psi_I \bar{\boldsymbol v} d\Gamma + \alpha_\theta \int_{\Gamma_\theta} \Psi_{I,\eta} n^\eta \boldsymbol a_3 \boldsymbol \bar \theta_{\boldsymbol n} d\Gamma + \alpha_C [[\Psi_I \boldsymbol a_3 \boldsymbol a_3 \cdot \bar{\boldsymbol v}]]_{\boldsymbol x \in C_v}

Comparing with the consistent terms of Eqs (\ref{de2}) and (\ref{nde2}), their expression is almost identical, the major difference is that the higher order derivatives of shape functions have been replaced by smoothed gradients. Owing to the reproducing kernel framework, the construction of smoothed gradients only concerns about the computation of traditional meshfree shape functions and their first order derivatives, which avoids the costly computation of higher order derivatives. Moreover, the stabilized terms in Eq. (\ref{nd3}) employs the penalty method to ensure the coercivity of stiffness, in contrast, the stabilized term of Eq. (\ref{de3}) naturally exist in weak form, and it can stabilize the result without any artificial parameters.

### 2024-02-14 conclusion.tex
last night

\section{Conclusion}\label{conclusion}
An efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions. In this approach, the mixed formulation with Hu-Washizu principle weak form is employed, where the displacement is discretized by traditional meshfree shape functions, the strains and stresses can be expressed by reproducing kernel smoothed gradients and covariant smoothed gradients. The smoothed gradient naturally embed the first two order integration constraint, and has a quasi variational consistency for curved models in each integration cells. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with conventional Nitsche's method, both have the consistent term and stabilized term. Compared with Nitsche's method, the costly high order derivatives in Nitsche's consistent term have been replaced by smoothed gradients, which shows great computational speed due to the reproducing kernel gradient smoothing framework. Meanwhile, the stabilized term is naturally existed in Hu-Washizu weak form, and the artificial parameter needed in Nitsche's stabilized term has been vanished, which can automatically maintain the coercivity for stiffness matrix. Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability

>>>>

\section{Conclusion}\label{conclusion}
An efficient and quasi-consistent meshfree thin shell formulation was presented to naturally enforce the essential boundary conditions. In this approach, the mixed formulation with Hu-Washizu principle weak form is employed, where the displacement is discretized by traditional meshfree shape functions, the strains and stresses can be expressed by reproducing kernel smoothed gradients and covariant smoothed gradients. The smoothed gradient naturally embed the first two order integration constraint, and has a quasi variational consistency for curved models in each integration cells. Owing to the Hu-Washizu variational principle, the essential boundary condition enforcement has a similar form with conventional Nitsche's method, both have the consistent term and stabilized term. Compared with Nitsche's method, the costly high order derivatives in Nitsche's consistent term have been replaced by smoothed gradients, which shows great computational speed due to the reproducing kernel gradient smoothing framework. Meanwhile, the stabilized term is naturally existed in Hu-Washizu weak form, and the artificial parameter needed in Nitsche's stabilized term has been vanished, which can automatically maintain the coercivity for stiffness matrix. Numerical results demonstrated that the proposed Hu-Washizu quasi-consistent meshfree thin shell formulation show great performance in terms of accuracy, efficiency and stability.
